Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-03-17 ms.tex
more work on sections 2 and 3

 \section{Data}
\label{sec:data}
All \PLANCK~data products utilized throughout this work are drawn from the 
\PLANCK~2013 release \citep{planck2013}. Specifically, we have made use 
of the 217 GHz, 353 GHz, 545 GHz and 857 GHz intensity maps which have been 
corrected for zodiacal light 
\citep[\texttt{R1.10\_nominal\_ZodiCorrected},][]{planckzodi}.

@@

\subsection{CMB Anisotropy Removal}
\label{sec:cmb}
We first addressed the CMB anisotropies before performing any of the 
interpolation/smoothing described in $\S$\ref{sec:ptsrc}/$\S$\ref{sec:smth}. 
The CMB anisotropies are effectively imperceptible in \PLANCK~857 GHz, but can 
be perceived at a low level in \PLANCK~545 GHz, and are prominent in 
\PLANCK~217 GHz and 353 GHz relative to the Galactic emission we wish to 
characterize, especially at high latitudes. To remove the CMB anisotropies, we 
have subtracted the Spectral Matching Independent Component Analysis 
(\verb|SMICA|) model from each of the \PLANCK~maps \citep{smica}, after 
applying appropriate unit conversions. Removal of the residual Solar dipole at 
low frequencies is discussed in $\S$\ref{sec:zp}.
% SMICA is subtracted from ALL Planck maps being used, including 545, 857 GHz
% WHAT IS THE ANGULAR RESOLUTION OF THE SMICA MAP, AND IS IT EVEN
% WELL-DEFINED??

\subsection{Compact Sources}
\label{sec:ptsrc}
%start by mentioning that SFD removed compact sources (outside of b +/- 5)
After subtracting the \verb|SMICA| CMB model, we next proceeded to interpolate 
over compact sources, including both point sources and resolved galaxies. 
Removing compact sources at this stage is important as it prevents 
contamination of compact-source-free pixels in our downstream analyses which 
require smoothing of the \PLANCK~maps. SFD carefully removed point sources and 
galaxies from the \verb|i100| map everywhere outside of 
$|b|$$<$$5^{\circ}$. We do not perform any further modifications of the 
\verb|i100| map to account for compact sources. To mask compact sources in the 
\PLANCK~maps, we use the SFD compact source mask, which was originally 
constructed to mask point sources and resolved compact objects that are not 
part of the Galactic cirrus at 3000 GHz. Given our pixelization (see 
$\S$\ref{sec:pix}), 1.56\% of pixels are masked.

@@

\subsection{Smoothing}
\label{sec:smth}
We wish to simultaneously fit \verb|i100| along with the four 
highest-frequency \PLANCK~bands. To properly combine these maps, they must have
 the same point spread function (PSF). \verb|i100|, with its $6.1'$ symmetric 
Gaussian PSF, is the lowest-resolution map we have included. To match PSFs, we 
have therefore smoothed each of the \PLANCK~maps under consideration to $6.1'$ 
resolution by considering each native map to have a symmetric Gaussian beam and
 smoothing by the appropriate symmetric Gaussian such that the resulting map 
has a FWHM of $6.1'$. The FWHM we assign to the native \PLANCK~maps is taken 
from \cite{planckbeam}, specifically $5.01'$ for 217 GHz, $4.86'$ for 353 GHz, 
$4.84'$ for 545 GHz, and $4.63'$ for 857 GHz.

>>>>

 \section{Data}
\label{sec:data}
All \PLANCK~data products utilized throughout this work are drawn from the 
\PLANCK~2013 release \citep{planck2013}. Specifically, we have made use 
of all six of the zodiacal light corrected HFI intensity maps
\citep[\texttt{R1.10\_nominal\_ZodiCorrected},][]{planckzodi}. Our 
full-resolution (6.1$'$ FWHM) SED fits neglect the two lowest HFI frequencies, 
100 and 143 GHz, as these have FWHM of 9.66$'$ and 7.27$'$ respectively.

@@

\subsection{CMB Anisotropy Removal}
\label{sec:cmb}
We first addressed the CMB anisotropies before performing any of the 
interpolation/smoothing described in $\S$\ref{sec:ptsrc}/$\S$\ref{sec:smth}. 
The CMB anisotropies are effectively imperceptible upon visual inspection 
in \PLANCK~857 GHz, but can be perceived at a low level in \PLANCK~545 GHz, and
are prominent from 100 to 353 GHz relative to the Galactic emission
we wish to characterize, especially at high latitudes. To remove the CMB 
anisotropies, we have subtracted the Spectral Matching Independent Component 
Analysis \citep[SMICA,][]{smica} model from each of the \PLANCK~maps, 
after applying appropriate unit conversions for the 545 and 857 GHz maps 
with native units of MJy/sr. Low-order corrections, particularly removal of the
residual Solar dipole, are discussed in $\S$\ref{sec:zp}.
% SMICA is subtracted from ALL Planck maps being used, including 545, 857 GHz
% WHAT IS THE ANGULAR RESOLUTION OF THE SMICA MAP, AND IS IT EVEN
% WELL-DEFINED??

\subsection{Compact Sources}
\label{sec:ptsrc}
%start by mentioning that SFD removed compact sources (outside of b +/- 5)
After subtracting the SMICA CMB model, we next proceeded to interpolate 
over compact sources, including both point sources and resolved galaxies. 
Removing compact sources at this stage is important as it prevents 
contamination of compact-source-free pixels in our downstream analyses which 
require smoothing of the \PLANCK~maps. SFD carefully removed point sources and 
galaxies from the \verb|i100| map everywhere outside of 
$|b|$$<$$5^{\circ}$. We do not perform any further modifications of the 
\verb|i100| map to account for compact sources. To mask compact sources in the 
\PLANCK~maps, we use the SFD compact source mask, which was originally 
constructed to mask point sources and resolved compact objects that are not 
part of the Galactic cirrus at 3000 GHz. Given our pixelization (see 
$\S$\ref{sec:pix}), 1.56\% of pixels are masked.

@@

\subsection{Smoothing}
\label{sec:smth}
For our full-resolution model,  wish to simultaneously fit \verb|i100| along 
with the four highest-frequency \PLANCK~bands. To properly combine these maps, 
they must have the same point spread function (PSF). \verb|i100|, with its 
$6.1'$ symmetric Gaussian beam, has the lowest angular resolution of the 
relevant maps. To match PSFs, we have therefore smoothed each of the 
\PLANCK~maps under consideration to $6.1'$ resolution by considering each 
native map to have a symmetric Gaussian beam and smoothing by the appropriate 
symmetric Gaussian such that the resulting map has a FWHM of $6.1'$. The FWHM 
we assign to the native \PLANCK~maps is taken from \cite{planckbeam}, 
specifically $5.01'$ for 217 GHz, $4.86'$ for 353 GHz, $4.84'$ for 545 GHz, and
$4.63'$ for 857 GHz.
